PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-18 qfenv_paper/qf_environment.tex
New figures and edits on qf calculation section

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primuszerr_masslimit_edgecut_histogram.png,height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 1.5$ and high density environment $n_{\rm{env}} > 3.5$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments. }      \label{fig:envcount}
    \end{center}
\end{figure*}

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.

With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.25$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading: darker with lower redshift. In order to calculate the uncertainty for the quiescent fraction, we follow the same steps in the standard jackknife technique as we did for the SMF in Section \ref{sec:smfcalc}. We represent the quiescent fraction uncertainty by the width in Figure \ref{fig:qf}.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results strongly agree with the observed decline of global star-formation in the universe (\cite{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, we find that this mass decreases over cosmic time. This corresponds to the well-known mass-downsizing pattern in the literature (e.g. \cite{bundy06a}). Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}). %Remark on how the M_{50-50}? is lower for high environment f_{Q}, and that it generally increases with redshift. A trend also observed in the t_{5050} considerations.

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ values for low and high environments are consistent with previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment for SDSS galaxies. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lowest mass bin ($\rm{log} \; \mathcal{M} \sim 10.2$).

@@

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments. Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results are generally consistent with our $f_{\rm{Q}}$ at high and low density environments.

Additionally, the zCOSMOS results indicate that the $f_{\rm{red}}$ values in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmass10_5_lit_primuszerr.eps, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot)$, for low (square) and high (circle) density environments within the redshift range $z = 0.0 - 0.8$.  There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. However the difference in $f_{Q}(\mathcal{M}_{\rm{fid}})$ for the two environments remains constant throughout suggesting that while the quiescent fraction is higher in dense environments, the evolution of the quiescent fraction is independent of environment.}         \label{fig:qffit}
    \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{10^{10.5} \: \mathcal{M}_{\odot}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). The value $10^{10.5} \: \mathcal{M}_{\odot}$ in the equation represents an empirically selected fiducial mass $\mathcal{M}_{\rm{fid}}$ within the stellar mass limits where there is a sufficiently large number of galaxies. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (diamond) and high (circle) density environments.

\begin{table} 
  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &$n_{\rm{env}} < 0.5$           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
               &$n_{\rm{env}} > 3$            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf}.  
\end{table}

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. For $z < 1.0$, galaxy populations in higher density environments have higher quenched fractions. As galaxy color and SFR are related, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) in favor of the idea that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).

>>>>

In order to quantify the effects of these photometric underestimations in our analysis, we replace our SDSS fluxes in the $ugriz$ band with $ugriz$ fluxes from the NASA-Sloan Atlas (NSA) catalog, which incorporate the improved background subtraction presented in \cite{Blanton:2011aa} and uses single-Seric fit fluxes rather than the standard SDSS \texttt{cmodel} fluxes. Using the ratio of the luminosity derived from the improved photometry over the luminosity derived from the standard SDSS VAGC photometry, we impose a preliminary correction on the stellar mass values obtained from \texttt{iSEDfit} assuming a consistent mass-to-light ratio. This mass correction leads to a significant increase in the stellar mass function for $\mathcal{M} > 10^{11} \mathcal{M}_{\odot}$ that matches the results from \cite{Bernardi:2013aa}. However, the effect of the mass correction was negligible for the quiescent fraction evolution results. As a result, we do not discuss the issues with photometric measurements any further in this paper. The effects of the discussed photometry methods on the luminosity function and stellar mass function will be examined in detail in future work. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY SAMPLE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Galaxy Sample} \label{sec:target} 
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections of by the environment classification cutoffs (vertical black lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $56.0 \%$ of galaxies in the redshift bin have low density environments while $29.0\%$ of galaxies in the redshift bin have high density environments. }      \label{fig:envcount}
    \end{center}
\end{figure*}

@@

\begin{figure*}
    \begin{center}
        \leavevmode
        \epsfig{file=fig_qf_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_lit_primuszerr.eps, height=0.75\textwidth,angle=90}
        \caption{Evolution of the quiescent fraction $f_{\rm{Q}}$ for galaxies in low (left) and high (rights) density environments for $z < 0.8$. $f_{\rm{Q}}$s were calculated using the SMFs in Figure\ref{fig:smf}, as described in text. Darker shading indicates lower redshift and the width represents the standard jackknife uncertainty.}         \label{fig:qf}
    \end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Quiescent Fraction} \label{sec:qf_const}
The SMFs calculated in the previous section illustrate the stellar mass distribution of our galaxy population and its evolution over comic time. In this section, using the SMFs of our subsamples, we compare the quiescent and the star-forming populations by calculating the fraction of galaxies that have quenched their star-formation, the quiescent fraction.

With the sufficient statistics available from SDSS and PRIMUS, we evaluate the quiescent fraction in bins of stellar mass and redshift for low and high density environments (Section \ref{sec:qfevol}). More specifically, by analyzing the quiescent fraction with respect to mass, redshift, and environment we are able to compare the quiescent fraction evolution in low and high density environments. Through this comparison, in Section \ref{sec:env_qf_evol}, we reveal the subtle environmental effects in quenching star formation that are often obscured by the underlying correlations among galactic properties such as color-mass and mass-density relations (\cite{Cooper:2010aa}). Furthermore by quantifying the environmental effects of star-formation quenching, we are able to provide constraints on the various proposed environmental quenching mechanisms, such as strangulation and ram-pressure stripping (\cite{McCarthy:2008aa}).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% EVOLUTION OF THE QUIESCENT FRACTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Evolution of the Quiescent Fraction} \label{sec:qfevol}
From the SMF number densities ($\Phi$) computed in the previous section, the quiescent fraction is computed as follows, 
\begin{equation}
f_{\rm{Q}} = \frac{\Phi_{Q}}{\Phi_{SF}+\Phi_{Q}}.
\end{equation}
$\Phi_{Q}$ and $\Phi_{SF}$ are the total number of galaxies per unit volume in stellar mass bin of $\Delta(\rm{log} \: \mathcal{M}) = 0.20 \: {\it dex}$ for the quiescent and star-forming subsamples, respectively (Equation \ref{eq:phi}). We compute $f_{\rm{Q}}$ for high and low density environments for all redshift bins as plotted in Figure \ref{fig:qf}, which shows the evolution of $f_{\rm{Q}}$ for high (right) and low (left) density environments. As in Figure \ref{fig:smf}, the evolution of the quiescent fraction over cosmic time is represented in the shading (darker with lower redshift) and the uncertainty is represented by the width. We use the standard jackknife technique, following the same steps as the SMF uncertainty in Section \ref{sec:smfcalc}, in order to calculate the uncertainty for the quiescent fraction.

@@

Focusing on the redshift evolution of $f_{\rm{Q}}$, we find that for both environments $f_{\rm{Q}}$ increases as redshift decreases. For high density environment, this is analogous to the Butcher-Omeler Effect (\cite{Butcher:1984aa}), which states that galaxy populations in groups or clusters have higher $f_{\rm{blue}}$, or lower $f_{\rm{Q}}$, at higher redshift. For all environments a larger portion of our galaxy population has quenched its star-formation over time. Coupled with the decline of SFR in the star-forming population (\cite{Noeske:2007aa}; \cite{cooper08a}), our results are in agreement with the observed decline of global star-formation in the universe (\cite{hopkins06a}). %Maybe Stacey et al. 2014 is relevant here?

In addition, when we compare the stellar masses at which $f_{\rm{Q}} = 0.5$ for each subsample, the so-called $\mathcal{M}_{50-50}$, we find that this quantity decreases over cosmic time. This corresponds to the well-known mass-downsizing pattern in the literature (e.g. \cite{bundy06a}). Furthermore, the mass-downsizing trend observed in each of our environment subsample is consistent with the trend observed in zCOSMOS Redshift Survey for isolated and group galaxies (\cite{Iovino:2010aa}). %Remark on how the M_{50-50}? is lower for high environment f_{Q}, and that it generally increases with redshift. A trend also observed in the t_{5050} considerations.

Finally, we compare our $f_{\rm{Q}}$ results to previous $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements for analogous environment classifications. For our lowest redshift bin, we find that our $f_{\rm{Q}}$ for low and high environments are consistent with previous SDSS $f_{\rm{Q}}$ (or $f_{\rm{red}}$) measurements as a function of environment. For example, \cite{Tinker:2011aa}, using a group-finding algorithm on the SDSS DR7, presents the relationship between $f_{\rm{Q}}$ and overdensity for galaxies within the mass range $\rm{log} \; \mathcal{M} = [9.8, 10.1]$. The \cite{Tinker:2011aa} $f_{\rm{Q}}$ at the lowest and highest overdensities, $f_{\rm{Q}} \sim 0.4$ and $f_{\rm{Q}} \sim 0.6$ respectively, are consistent with our $f_{\rm{Q}}$ for low and high density environment at the lower mass limit ($\rm{log} \; \mathcal{M} \sim 10.2$).

@@

For $z > 0.2$, we compare our PRIMUS $f_{\rm{Q}}$ results to the $f_{\rm{red}}$ (or $1-f_{\rm{blue}}$) results from the zCOSMOS Redshift Survey (\cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, \cite{Kovac:2014aa}), which approximately covers the same redshift range as PRIMUS. \cite{Iovino:2010aa}, \cite{Cucciati:2010aa}, and \cite{Kovac:2014aa} using a mass-complete galaxy sample derived from zCOSMOS and a group catalog, 3D local density contrast, and overdensity environment measurements, respectively, compare $f_{\rm{red}}$ with respect to environment. The $f_{\rm{blue}}$ for group and isolated galaxies from \cite{Iovino:2010aa} are generally inconsistent with our $1-f_{\rm{Q}}$ for high and low density environments.

Similarly, $f_{\rm{red}}$ for high and low overdensities in \cite{Kovac:2014aa} are  greater overall than the PRIMUS $f_{\rm{Q}}$ values in high and low density environments. However, \cite{Kovac:2014aa} points out that there is a significant difference between classifying the quenched population using color and SFR. For their lower redshift bin ($0.1 < z < 0.4$) they find that their $f_{\rm{Q}}$ defined by color is greater than $f_{\rm{Q}}$ defined by SFR by roughly $0.2$. And for their higher redshift bin ($0.4 < z < 0.7$) they find a difference of $0.15-0.19$. Although the propagation of this difference for different environments is not explored in \cite{Kovac:2014aa}, if we account for the difference uniformly for $f_{\rm{red}}$ at all environments, the \cite{Kovac:2014aa} results in their lower redshift bin ($0.1< z < 0.4$) are generally consistent with our $f_{\rm{Q}}$ at high and low density environments. In their higher redshift bin ($0.4 < z < 0.7$), even accounting for the difference in galaxy classification, \cite{Kovac:2014aa} finds a significantly higher $f_{\rm{Q}}$.

We previously addressed that for both low and high density environments, $f_{\rm{Q}}$ increases as redshift decreases. This general trend is in good agreement with\cite{Iovino:2010aa}, which finds a similar increase in $1-f_{\rm{red}}$ over cosmic time for $\mathcal{M} < 10^{10.9} \mathcal{M}_{\odot}$. However, our $f_{\rm{Q}}$ redshift evolution disagrees with \cite{Kovac:2014aa}, which presents a general decrease in $f_{\rm{red}}$ over cosmic time for low environment.

The zCOSMOS results also find that $f_{\rm{red}}$ in high density environments are greater overall than in low density environments. The same trend is observed in the PRIMUS results and will be discussed in detail later in Section \ref{sec:env_qf_evol}. Another significant trend observed in the zCOSMOS results is the significant mass dependence of the $f_{\rm{red}}$ and $f_{\rm{blue}}$ evolution. \cite{Iovino:2010aa} by examining $f_{\rm{blue}}(z)$ in different mass bins for group and isolated galaxies find significantly larger $f_{\rm{blue}}$ evolution at lower masses. In fact, \cite{Iovino:2010aa} finds no evolution in $f_{\rm{blue}}$ for $\mathcal{M} > 10^{10.9} \mathcal{M}_{\odot}$ for both group and isolated galaxies over the redshift range $0.4 < z < 0.9$. On the other hand, in the lowest mass bin ($10^{10.0} \mathcal{M}_{\odot} < \mathcal{M} < 10^{10.5} \mathcal{M}_{\odot}$) \cite{Iovino:2010aa} finds $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.2$ for isolated galaxies and  $f_{\rm{blue}}(z \sim 0.4) - f_{\rm{blue}}(z \sim 0.2) \sim 0.1$ for group galaxies. In contrast, in each of the panels of Figure \ref{fig:qf}, we qualitatively find little mass dependence on the $f_{\rm{Q}}$ evolution for either low or high density environments. However, due to the distinct stellar mass completeness limits imposed at each redshift bin of our sample, subtle effects such as the mass dependence of the $f_{\rm{Q}}$ evolution are difficult to discern.

\begin{figure}
    \begin{center}
        \leavevmode
        \epsscale{1.0}
        \epsfig{file=fig_qffit_cylr2h25_thresh75_bin0_20_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_fidmasscomp11_0_10_5_lit_primuszerr.eps, height=0.45\textwidth}
        \caption{The evolution of the quiescent fraction at fiducial mass, $f_{Q}(\mathcal{M}_{\rm{fid}})$, for low (blue) and high (red) density environments within the redshift range $z = 0.0 - 0.8$. We present the $f_{Q}(\mathcal{M}_{\rm{fid}})$ evolution for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_\odot$ (solid fill) and $10^{11} \mathcal{M}_\odot$ (patterned fill) with the uncertainty of the best-fit parameter $b$ in Equation \ref{eq:qffit} represented by the width of the evolution. There is a significant increase in $f_{Q}(\mathcal{M}_{\rm{fid}})$ with decrease in redshift for both environments. In addition, over the entire redshift range, high density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$ is greater than low density environment $f_{Q}(\mathcal{M}_{\rm{fid}})$. For the environment cut-offs ($n_{\rm{env}} < 0.5$ for low and $n_{\rm{env}} > 3.0$ for high), there is no significant difference in the slope of the evolution between the environments.}         \label{fig:qffit}
    \end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ENVIRONMENTAL EFFECTS ON THE QUIESCENT FRACTION EVOLUTION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Environmental Effects on the Quiescent Fraction Evolution} \label{sec:env_qf_evol}
In order to more quantitatively compare the $f_{\rm{Q}}$ evolution for different epochs and environments, we fit $f_{\rm{Q}}$ for each subsample to a power-law parameterization as a function of stellar mass, 
\begin{equation} \label{eq:qffit}
f_{\rm{Q}}(\mathcal{M}_{*}) = a \: \rm{log} \; \left(\frac{ \mathcal{M}_{*}}{\mathcal{M}_{\rm{fid}}} \right)+b,
\end{equation}
where $a$ are $b$ are best-fit parameters using {\em MPFIT} (\cite{Markwardt:2009aa}). $\mathcal{M}_{\rm{fid}}$ represents the empirically selected fiducial mass within the stellar mass limits where there is a sufficiently large number of galaxies. We primarily focus on $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$. This fiducial mass serves to highlight and quantify the $f_{\rm{Q}}$ evolution for different redshifts. Figure \ref{fig:qffit} shows the evolution of $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ from $z \sim 0.7$ to $\sim 0.1$ for low (blue) and high (red) density environments for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \: \mathcal{M}_{\odot}$ (solid fill) and $10^{11} \: \mathcal{M}_{\odot}$ (pattern fill).

\begin{table} 
  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &$n_{\rm{env}} < 0.5$           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
               &$n_{\rm{env}} > 3$            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf} for $\mathcal{M}_{\rm{fid}} = 10^{10.5} \mathcal{M}_{\odot}$.
\end{table}

Figure \ref{fig:qffit} illustrates that throughout the entire redshift range, high density environment has a significantly greater $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ than the lower density environment. This is in strong agreement with the zCOSMOS results from \cite{Cucciati:2010aa} and \cite{Kovac:2014aa}. Galaxy populations in higher density environments at $z < 1.0$ have higher quenched fractions. As galaxy color serves as a proxy for SFR, our results support the existence of the color-density relation (\cite{Cucciati:2010aa}; \cite{Cooper:2010aa}) and debunk the suggestions that the color-density relation is a merely a reflection of the mass-density or morphology-density relation (\cite{Scodeggio:2009aa}, \cite{Tasca:2009aa}).

For $\mathcal{M}_{\rm{fid}} = 10^{11} \mathcal{M}_\odot$, aside from an overall shift in $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}})$ by $\sim 0.2$, we observe the same evolutionary trends. $f_{\rm{Q}}(\mathcal{M}_{\rm{fid}} = 10^{11}\mathcal{M}_{\odot})$ for both low and high density environments each increase by $\sim 0.2$ as redshift decreases from $\sim 0.7$ to $\sim 0.1$, keeping the slope the same. Evidently, increasing the fiducial mass to $10^{11} \mathcal{M}_{\odot}$ does not significantly alter the total evolution for either environments.
